---
title: "Demographic Equation"
author: "YOUR NAME HERE"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Demographic Equation

$$P_t = P_0 + (B - D) + (I - E)$$

## Load data and libraries

```{r,message=FALSE}
library(tidyverse)
data<-read_csv("data_be.csv")
```

## Calculate 2011 Prediction

King County Prediction in 2011 is $`r data$Population[1]`+`r data$Births[1]`-`r data$Deaths[2]`+(`r data$"In Migration"[2]`-`r data$"Out Migration"[2]`)=`r data$Population[1]+data$Births[1]- data$Deaths[2]+(data$"In Migration"[2]-data$"Out Migration"[2])`$

The Difference from the observed 2011 data is `r abs((data$Population[1]+data$Births[1]- data$Deaths[2]+(data$"In Migration"[2]-data$"Out Migration"[2]))-data$Population[2])`

## Calculate 2018 Prediction

**Your Code Here**

## Growth Curve For King County

```{r}
# Convert to time series
necessary_packages <- c("tidyverse", "forecast")

for (pkg in necessary_packages) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}


kc<-data%>%filter(Location=="King County")
ts_data <- ts(kc$Population, start = min(kc$Year), frequency = 1)

# Fit exponential model
exp_model <- nls(Population ~ a * exp(b * (Year - 2010)), data = kc,
                 start = list(a = min(data$Population), b = 0.01))

# Generate future years
future_years <- seq(2019, 2010 + 500, by = 1)
future_pop <- predict(exp_model, newdata = data.frame(Year = future_years))

# Plot
# Create a forecast data frame
forecast_data <- data.frame(Year = future_years, Population = future_pop)

# Plot
ggplot() +
  geom_point(data = kc, aes(x = Year, y = Population), color = "blue") +
  geom_line(data = kc, aes(x = Year, y = Population), color = "blue") +
  geom_line(data = forecast_data, aes(x = Year, y = Population), color = "red", linetype = "dashed") +
  labs(title = "Exponential Forecast of King County Population (Next 500 Years)",
       x = "Year", y = "Population") +
  theme_minimal()

```

## Growth Curve For Los Angeles

**Your Code Here**

## IMR and Probability

Take the IMR numbers from google sheets and compute them using R Code in the R Chunk below:

```{r}

```


